### 2021-04-05 manuscript.Rmd
move manuscript to project root

# Link to the bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Source plotting functions
source("analysis/manuscript_files/functions_plots_tables.R")

# Create an export folder for results
dir.create("analysis/export", showWarnings = FALSE)

@@

# Backup epochs to the export folder
epochs_exp1$save("analysis/export/exp1-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("analysis/export/exp1-objects.tsv")

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_tsv("analysis/export/montage.tsv")

@@

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp1

@@

# Compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp1,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
```

```{r exp1-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp1

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
```

@@

# epochs = preproc(
#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
#   metadata=r.data_exp1.query("participant == 'VP_04'"),
#   n_components=15,
#   method="fastica",
#   l_freq=None,
#   h_freq=None,
#   event_id=dict(match=221, mismatch=222),
#   tmin=-0.5,
#   tmax=1.498,
#   baseline=(-0.2, 0),
#   reject=dict(eeg=200)
# )
# epochs.save("analysis/export/vp04-epo.fif")

epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load sample time points and electrode montage
montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())

@@

# Backup epochs to the export folder
epochs_exp2$save("analysis/export/exp2-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp2-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("analysis/export/exp2-objects.tsv")

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
```

```{r exp2-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp2)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-models.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("analysis/export/joint-models.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_control,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")

@@

# Preprocess the EEG for Experiment 3 in Python
fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
py_run_string(
  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
)
message("This worked!!!")
py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
message("This also worked!!!")
py_run_string("epochs_exp3.save('analysis/export/exp3-epo.fif', overwrite=True)")
py_run_string("del epochs_exp3")

@@

# Backup epochs to the export folder
epochs_exp3$save("analysis/export/exp3-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp3-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp3, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
  write_tsv("analysis/export/exp3-objects.tsv")

@@

```{r exp3-models, eval=run_exp3}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    position = factor(position, levels = c("Inverted", "Upright")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions and parts
  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
  droplevels() -> data_exp3

@@

# Compute the models for Experiment 3
map(
  comps$name,
  compute_models,
  formula = formula_exp3,
  data = data_exp3,
  control = control,
  specs = specs_exp3
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
```

>>>>

# Link to the bibliography file
r_refs("manuscript_files/r-references.bib")

# Source plotting functions
source("manuscript_files/functions_plots_tables.R")

# Create an export folder for results
dir.create("export", showWarnings = FALSE)

@@

# Backup epochs to the export folder
epochs_exp1$save("export/exp1-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  write_tsv("export/exp1-data.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("export/exp1-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("export/exp1-objects.tsv")

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_tsv("export/montage.tsv")

@@

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp1

@@

# Compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp1,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("export/exp1-models.RDS") -> models_exp1
```

```{r exp1-import}
# Load average number of objects per condition
(read_tsv("export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

# Load preprocessed single-trial data
read_tsv("export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp1

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("export/exp1-gaverages.RDS")
models_exp1 <- readRDS("export/exp1-models.RDS")
```

@@

# epochs = preproc(
#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
#   metadata=r.data_exp1.query("participant == 'VP_04'"),
#   n_components=15,
#   method="fastica",
#   l_freq=None,
#   h_freq=None,
#   event_id=dict(match=221, mismatch=222),
#   tmin=-0.5,
#   tmax=1.498,
#   baseline=(-0.2, 0),
#   reject=dict(eeg=200)
# )
# epochs.save("export/vp04-epo.fif")

epochs = mne.read_epochs("export/unf-exp1-epo.fif")

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load sample time points and electrode montage
montage <- read_tsv("export/montage.tsv", col_types = cols())

@@

# Backup epochs to the export folder
epochs_exp2$save("export/exp2-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  write_tsv("export/exp2-data.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("export/exp2-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("export/exp2-objects.tsv")

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("export/exp2-models.RDS") -> models_exp2
```

```{r exp2-import}
# Load average number of objects per condition
(read_tsv("export/exp2-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp2)

# Load preprocessed single-trial data
read_tsv("export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("export/exp2-gaverages.RDS")
models_exp2 <- readRDS("export/exp2-models.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("export/joint-models.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("export/joint-models.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_control,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("export/joint-control-models.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("export/joint-control-models.RDS")

@@

# Preprocess the EEG for Experiment 3 in Python
fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
py_run_string(
  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
)
message("This worked!!!")
py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
message("This also worked!!!")
py_run_string("epochs_exp3.save('export/exp3-epo.fif', overwrite=True)")
py_run_string("del epochs_exp3")

@@

# Backup epochs to the export folder
epochs_exp3$save("export/exp3-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
  write_tsv("export/exp3-data.tsv") -> data_exp3

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
  saveRDS("export/exp3-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp3, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
  write_tsv("export/exp3-objects.tsv")

@@

```{r exp3-models, eval=run_exp3}
# Load preprocessed single-trial data
read_tsv("export/exp3-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    position = factor(position, levels = c("Inverted", "Upright")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions and parts
  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
  droplevels() -> data_exp3

@@

# Compute the models for Experiment 3
map(
  comps$name,
  compute_models,
  formula = formula_exp3,
  data = data_exp3,
  control = control,
  specs = specs_exp3
) %>%
  set_names(comps$name) %T>%
  saveRDS("export/exp3-models.RDS") -> models_exp3
```
